If you have experience with Unity G\-U\-I\-Skins then you probably already know how to modify the default G\-U\-I. Simply make a new G\-U\-I\-Skin and apply it to the Virtual Piggy Skin value on \hyperlink{class_virtual_piggy_g_u_i}{Virtual\-Piggy\-G\-U\-I}. If you're not experienced with Unity's G\-U\-I\-Skins, continue reading.

If you'd like to change the look of the G\-U\-I included with the Plugin, you have a couple of choices. Included is a G\-U\-I\-Skin already put together for you. This is located in Plugins $>$ \hyperlink{class_virtual_piggy}{Virtual\-Piggy} $>$ Skin You may also create your own G\-U\-I\-Skin.

If you want to use your own G\-U\-I\-Skin, all you need to do is create a new G\-U\-I\-Skin and apply it to \hyperlink{class_virtual_piggy_g_u_i}{Virtual\-Piggy\-G\-U\-I}. You'll want to edit the Button, Label and Text\-Field elements.

The \hyperlink{class_virtual_piggy_g_u_i}{Virtual\-Piggy\-G\-U\-I} object also uses 16 custom styles. The easiest way to maintain the references to these is to Duplicate one of the existing G\-U\-I\-Skins. Then all you need to do is swap in the textures/fonts you want to use. The styles that this skin uses are\-: Login Button, Transaction\-Message, Success\-Indicator, fail\-Indicator, progress\-Indicator, fader, Transaction\-Ask\-Message, close\-Login, Yes\-Button, No\-Button, logo\-Backer, bg-\/border, bg, required\-Text, Login\-Text and grey\-Line.

If you want to scale the size of the gui \hyperlink{class_virtual_piggy_g_u_i}{Virtual\-Piggy\-G\-U\-I} has a \char`\"{}gui\-Scale\char`\"{} member that you can use adjust. 